Management induced changes of soil organic carbon on global croplands

### 2020-07-14 SOCbudgetPaper/SOCbudget.Rmd
small update on written paper part

---
title: Historical Soil Organic Carbon Budget
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'communication')`"
author:
  - given_name: Kristine
    surname: Karstens
    affiliation: 1
    email: kristine.karstenst@pik-potsdam.de
    corresponding: true
  - given_name: Benjamin Leon
    surname: Bodirsky
    affiliation: 1
  - given_name: Alexander
    surname: Popp
    affiliation: 1
affiliation:
  - code: 1
    address: Potsdam-Institut of Climate Impacts Research, Potsdam, Germany
abstract: | 
 SOC one of larges c sinks on earth (3 times larger biospehre pool). Agricultural management leads to a depletion of soil organic crabon. However
 this depletion of soil organic carbon (SOC) pools are so far not well represented in global assessments of historic carbon emissions. While SOC
 models often represent well the biochemical processes that lead to the accumulation and decay of SOC, the management decisions driving these 
 biophysical processes are still little investigated.
 Here we create a spatial explicit data set for crop residue and manure management on cropland based on global historic production (FAOSTAT) and 
 land-use (LUH2) data and combine it with the IPCC Tier 2 approach to create a half-degree resolution soil organic carbon budget on mineral soils.
 We estimate that due to arable farming soils have lost over (?) GtOC of which (??) GtOC have been released within the period 1990-2010.
 Tier 2 IPCC methodolgy estimates higher soil organic carbon losses than Tier 1 methods, which may origin from … . We also find that SOC is very 
 sensity to management decision such as residue recycling indicating the nessessity to incorporated better management data in soil models. 
bibliography: SOCbudget.bib
running:
  title: R Markdown Template for Copernicus
  author: Nüst et al.
competinginterests: |
  The authors declare no competing interests.
# OPTIONAL:
algorithms: true
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed.
copyrightstatement: |
  The author's copyright for this publication is transferred to institution/company.
availability:
  codedata: |
    use this to add a statement when having data sets and software code available
authorcontribution: |
  Karstens wrote code and paper build on work of Bodirsky. Bodirsky and Popp revised paper.
disclaimer: |
  We like Copernicus.
acknowledgements: |
  Thanks to the rticles contributors!
appendix: |
  \section{Figures and tables in appendices}
  \subsection{Option 1}
  If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
  They will be correctly named automatically.
  \subsection{Option 2}
  If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.

@@

  Please add `\clearpage` between each table and/or figure. Further guidelines on figures and tables can be found below.
  Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:
  To rename them correctly to A1, A2, etc., please add the following commands in front of them:
output:
  rticles::copernicus_article: default
  bookdown::word_document2: default
  md_document:
    variant: markdown_github
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
    md_extensions: +raw_attribute
---
\newpage

>>>>

---
title: Management induced changes of soil organic carbon on global croplands 
       \newline or \newline
       How management changed soil organic carbon on global croplands
       \newline or \newline
       Agricultural soil have lost 13 GtC topsoil carbon
       \newline or \newline
       Linking agricultural management data to soil modeleling – a global approach

journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'communication')`"
author:
  - given_name: Kristine
    surname: Karstens
    affiliation: 1
    email: kristine.karstens@pik-potsdam.de
    corresponding: true
  - given_name: Benjamin Leon
    surname: Bodirsky
    affiliation: 1
  - given_name: Your
    surname: Name
    affiliation: 2
  - given_name: Alexander
    surname: Popp
    affiliation: 1
affiliation:
  - code: 1
    address: Potsdam-Institut of Climate Impacts Research, Potsdam, Germany
  - code: 2
    address: Your affiliation 
abstract: | 
  Soil organic carbon (SOC) is one of larges c stocks on earth (3 times larger biosphere pool). 
bibliography: SOCbudget.bib
running:
  title: R Markdown Template for Copernicus
  author: Nüst et al.
competinginterests: |
  The authors declare no competing interests.
# OPTIONAL:
algorithms: true
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed.
copyrightstatement: |
  The author's copyright for this publication is transferred to institution/company.
availability:
  codedata: |
    use this to add a statement when having data sets and software code available
authorcontribution: |
  Karstens wrote code and paper build on work of Bodirsky. Bodirsky, <here_could_be_your_names> and Popp revised paper.
disclaimer: |
  We like Copernicus.
acknowledgements: |
  Thanks to the rticles contributors!
appendix: |
  \section{Figures and tables in appendices}
  \subsection{Option 1}
  If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
  They will be correctly named automatically.
  \subsection{Option 2}
  If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.

@@

  Please add `\clearpage` between each table and/or figure. Further guidelines on figures and tables can be found below.
  Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:
  To rename them correctly to A1, A2, etc., please add the following commands in front of them:
output:
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
    md_extensions: +raw_attribute
  md_document:
    variant: markdown_github
  bookdown::word_document2: default
  bookdown::pdf_document2: default
  rticles::copernicus_article: default
---
\newpage
